\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}

\linespread{1.25}
\extrawidth{.75in}
\setlength\linefillheight{.5in}

\pagestyle{headandfoot}

\runningheadrule
\firstpageheader
    {CSC 212 / URI}
    {Final Exam}
    {Dec 19, 2020}
\runningheader
    {CSC 212 / URI}
    {Final Exam, Page \thepage\ of \numpages}
    {Dec 19, 2020}
\firstpagefooter
    {}
    {}
    {}
\runningfooter
    {}
    {}
    {}

\begin{document}

~{\large
    \vspace{.5in}

    This exam has \numquestions\ questions, for a total of \numpoints\ points.  You have 2.5 hours to complete the exam.  Please read carefully the guidelines below:

    \begin{itemize}
        \item[-] Your submission to Gradescope must include the following files:
        \begin{enumerate}
            \item A text file named \verb|XXXX.txt|, where \verb|XXXX| are the last four digits of your {\bf student ID}.  \underline{This file is the most important} as it will be used for {\bf grading} your work.  This file must contain your final answers to all questions, one per line.  If you don't have an answer, you can leave the line empty.  A template is provided at: \url{https://homepage.cs.uri.edu/~malvarez/stationary/exam/ans.txt}.
            \item A PDF file named \verb|XXXX.pdf|, where \verb|XXXX| are the last four digits of your {\bf student ID}.  This file will contain your work.  You can write your solutions on your own paper(s) and then scan or photograph them into a single PDF.  Do not worry about alignment or format, as long as your work is readable. In this file, your work on each question can be in any order.
        \end{enumerate}
        \item[-] If the question is multiple choice, the answer {\bf must be} the corresponding letter (A, B, C, ...).  If the question is open, the answer will be a single number, or as otherwise specified in the question.
        \item[-] You may use any of our lecture notes, books, or additional written/online references.  However, when solving the questions, your solution must follow the algorithms and formulas introduced in our lectures.
    \end{itemize}
    
    By submitting my solutions to this exam I acknowledge that I have read and understood the guidelines above, that all answers are my own, and that I have neither gained unfairly from others nor have I assisted others in obtaining an unfair advantage.
}
